A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-18 MSRChallenge2016.tex
Revert "Minor changes"
This reverts commit 852719faa3b9e4fcbac144a287481316ec3db88d.

\begin{table}[!htb]
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
	\centering
	\begin{tabular}{lr} 
		\hline
		& \textbf{GitHub}\\
		\hline
		\#Buggy Files & 46,301,429 \\ 
		\#AMP Pattern & 901,083 \\
		\#MSM Pattern & 783,073 \\
		\#COM Pattern & 270,128 \\ 
		\#CBC Pattern & 1,959,377 \\  
		\#IAO Pattern & 1,308,006 \\  
		\#ANC Pattern & 1,340,561 \\  
		\#AOB Pattern & 128,016 \\  
		\#COB Pattern & 262,915 \\   
		\hline
	\end{tabular}
\end{table}
\todo{Ferdian: please add a column that shows the number sin terms of
  percentages, not just raw numbers.}

After running the bug pattern detection approach on Boa's dataset, I obtained
the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM,
COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%,
4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files. We can see that the
most common pattern among these patterns is CBC and the least common pattern is
AOB. If we assume that these patterns never appear together in the dataset,
these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
patterns that they use cover almost 30\% of real
patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
it is hard to believe that the remaining two patterns cover 15\% of buggy files,
especially 14.78\% is a number we get when we assume that the patterns that we
detect never appear together. Moreover, the percentage of each pattern is based
on imprecise approximation which is likely to represent an upper bound rather
than a lower bound. This suggests that common bug fixing patterns might not be
as common as it appeared to be.

>>>>

\begin{table}[!htb]
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
	\centering
	\begin{tabular}{lrr} 
		\hline
		& \textbf{\#Appearance} & \textbf{Percentage}\\
		\hline
		%Buggy Files & 46,301,429 \\ 
		AMP Pattern & 901,083 & 1.95\%\\
		MSM Pattern & 783,073 & 1.69\%\\
		COM Pattern & 270,128 & 0.58\%\\ 
		CBC Pattern & 1,959,377 & 4.23\%\\  
		IAO Pattern & 1,308,006 & 2.82\%\\  
		ANC Pattern & 1,340,561 & 2.90\%\\  
		AOB Pattern & 128,016 & 0.28\%\\  
		COB Pattern & 262,915 & 0.57\%\\   
		\hline
	\end{tabular}
\end{table}

After running the bug pattern detection approach on Boa's dataset, we obtained
the result shown in Table~\ref{tab:freqpattern}. It shows that the
most common pattern among these patterns is CBC and the least common pattern is
AOB. If we assume that these patterns never appear together in the dataset,
these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
patterns that they use cover almost 30\% of real
patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
it is hard to believe that the remaining two patterns cover 15\% of buggy files,
especially 14.78\% is a number we get when we assume that the patterns that we
detect never appear together. Moreover, the percentage of each pattern is based
on imprecise approximation which is likely to represent an upper bound rather
than a lower bound. This suggests that common bug fixing patterns might not be
as common as it appeared to be.
